---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Outliers bias the mean and variance estimates (SD, SE)

Categorical - Unusual values (which accounts for < 10% of the dataset)
  1. Combine all the unusuals into one category
  2. Delete
  
Continuous - use boxplots, histogram

&&
Univariate
  Use scale() to z score the data and look for any obs with +-3 => exclude
    z-scores are distance from the mean
  
Multivariate
  Mahalanobis - creates a distance from the centroid (mean of all means) - works for both uni & mulivariate
    DEF: Mahalanobis distance is a measure of the distance between a point P and a distribution D
  use chi-squared table, df = # variables used to calculate distance, use p < 0.001
  
Treatment:
  Delete
  Impute
  Capping
  Treat separately
  
Slightly different procedure for outliers in regression
  
```{r loading data}
cars <- miss.val.treat
cars %>% View()
colSums(is.na(cars))
```

```{r creating mahalanobis distance for continuous}

mahal.dist <- mahalanobis()

```

